---
title: "Por que vemos pessoas vacinadas com covid-19?"
output: learnr::tutorial
runtime: shiny_prerendered
---

<!-- A fazer: marcados com TO-DO -->

```{r setup, include=FALSE}
library(learnr)
library(tidyverse) #load only needed components?
library(questionr)
knitr::opts_chunk$set(echo = FALSE)
```
```{r general_parameters}
population_size = 1000
#TO-DO: percentual vacinado do Brasil
#TO-DO: Percentual real para vacina selecionada - fully
vacc_per_init = 27 #initial slider position for percentage of population vaccinated

#refs: https://www.nytimes.com/interactive/2021/08/12/science/covid-delta-breakthrough.html?smtyp=cur&smid=tw-nytimes
#REF: https://www.medrxiv.org/content/10.1101/2021.08.21.21261501v1.full.pdf 
#Vaxzevria/Fiocruz VE Fully vacc ADJUSTED Table S1
infected_if_vacc_prob = 0.30 #Probability of being vaccinated and still get covid if exposed enough to get covid unvaccinated.


```
```{r server_parameters_init, context="server"}
point_size = 2

observeEvent(input$vacc_per_a,{
  if(input$vacc_per_a !=input$vacc_per_b)
    updateSliderInput(inputId = "vacc_per_b", value = input$vacc_per_a)
})

observeEvent(input$vacc_per_b,{
  if(input$vacc_per_b !=input$vacc_per_a)
    updateSliderInput(inputId = "vacc_per_a", value = input$vacc_per_b)
})




```

```{r data}
population = tibble(x = runif(population_size)*99+1, 
                    y = runif(population_size)*99+1,
                    infected_if_vacc = sample(x = c(TRUE,FALSE),
                                              replace = TRUE,
                                              size = population_size,
                                              prob = c(infected_if_vacc_prob,1-infected_if_vacc_prob))
)
```



## Com vacina, sem vacina e covid-19

Cada elemento no gráfico abaixo representa uma pessoa. Todas elas foram expostas ao vírus tempo suficiente para se infectar caso não tenham tomado a vacina.

Usando o controle, você pode determinar quantas delas estão vacinadas.


```{r plot_vacc_non_vacc, context="server"}
output$plot_vacc_non_vacc <- renderPlot({
  #TO-DO:Gráfico WAFFLE
  vacc_per = input$vacc_per_a
  population %>% 
    mutate( vacc = x <= vacc_per) %>%
    ggplot(aes(x=x, y=y, color = vacc)) +
    geom_point(size = point_size) +
    theme_minimal()
  
})
```
```{r vacc_per_control, echo=FALSE}
plotOutput("plot_vacc_non_vacc")
sliderInput("vacc_per_a", "Percentual vacinado da população:", min = 0, max = 100, value = vacc_per_init)
```


<!-- #TO-DO:Texto explicando que mesmo com vacina pode covid -->
Mesmo com vacina, pode ter covid..... no gráfico abaixo, as pessoas com covid estão marcadas XYZ. Nesta simulação, todas as pessoas foram expostas ao vírus o suficiente para infectar-se.  Assim, todas as pessoas não vacinadas estão com covid-19. Já a maior parte das vacinadas, escaparam. O espaço das pessoas não vacinadas está bem mais cheio de infectados.  No entanto,  também vemos casos entre as vacinadas.     

```{r plot_vacc_non_vacc_covid, context="server"}
output$plot_vacc_non_vacc_covid <- renderPlot({
  #TO-DO:Gráfico WAFFLE Padronizado
  vacc_per = input$vacc_per_a
  population %>%
    mutate( vacc = x <= vacc_per, 
            infected = (!vacc | infected_if_vacc)) %>%  #infected, if not vacc or if vacc but still in prob.
    ggplot(aes(x=x, y=y, 
               color = vacc, #color indicates vaccinated or not - change
               alpha = infected)) +
    geom_point(size = point_size) +
    theme_minimal()
})
```
```{r vacc_non_vacc_covid, echo=FALSE}
plotOutput("plot_vacc_non_vacc_covid")
```


<!-- #TO-DO:Texto Introdução gráfico só com os doentes -->
Só os doentes / doentes "arrumados" - mostrar percentuais


```{r plot_covid_only, context="server"}
output$plot_covid_only <- renderPlot({
  #TO-DO:Arrumar em barras
  #TO-DO:Gráfico WAFFLE Padronizado
  #TO-DO:PERCENTUAIS DO TOTAL EM VALORES
  vacc_per = input$vacc_per_a
  population_size = nrow(population)
  
  points_dist = 100/sqrt(population_size) #target mean distance between points
  
  infected_population <- population %>%
    mutate( vacc = x <= vacc_per, 
            infected = (!vacc | infected_if_vacc)) %>% #infected, if not vacc or if vacc but still in prob.
    filter(infected)
  
  vacc_infected_n <- infected_population %>% group_by(vacc) %>%
    summarise(n = n())
  
  #heights X widths
  #choose column width so that the higher group reaches the top 
  number_of_cols = max(3,max(vacc_infected_n$n / sqrt(population_size))) # in columns
  col_width_dist = number_of_cols * points_dist
  infected_population %>%
    group_by(vacc) %>%
    mutate( x_bar = runif(n()) * col_width_dist  - vacc*col_width_dist,
            y_bar = runif(n()) * n()/number_of_cols * points_dist) %>%
    ungroup() %>%
    
    
    ggplot(aes(x=x_bar, y=y_bar, 
               color = vacc #color indicates vaccinated or not - change
               
    )) +
    geom_point(size = point_size) + #TO-DO: adjust size? 
    theme_minimal()
  
})
```
```{r covid_only, echo=FALSE}
plotOutput("plot_covid_only")
sliderInput("vacc_per_b", "Percentual vacinado da população:", min = 0, max = 100, value = vacc_per_init)
```

<!-- TO-DO:TEXTO SOBRE percentual, testes com 100%, calculo de equilibrio  -->

<!-- TO-DO:GRAFICO de percentual de cada população -->

## Código exemplo a partir daqui - apagar ao final


TESTE de SLIDER DUPLICADO

```{r synch test, echo=FALSE}
sliderInput("bins_a", "Number of bins:", min = 1, max = 50, value = 30)
sliderInput("bins_b", "Number of bins:", min = 1, max = 50, value = 30)
sliderInput("bins_c", "Number of bins:", min = 1, max = 50, value = 30)
plotOutput("distPlot")
```

```{r, context="server"}

observeEvent(input$bins_a,{
  if(input$bins_a !=input$bins_b)
    updateSliderInput(inputId = "bins_b", value = input$bins_a)
  if(input$bins_a !=input$bins_c)
    updateSliderInput(inputId = "bins_c", value = input$bins_a)
})

observeEvent(input$bins_b,{
  if(input$bins_b !=input$bins_a)
    updateSliderInput(inputId = "bins_a", value = input$bins_b)
  if(input$bins_b !=input$bins_c)
    updateSliderInput(inputId = "bins_c", value = input$bins_b)
})
observeEvent(input$bins_c,{
  if(input$bins_c !=input$bins_a)
    updateSliderInput(inputId = "bins_a", value = input$bins_c)
  if(input$bins_c !=input$bins_b)
    updateSliderInput(inputId = "bins_b", value = input$bins_c)
})


output$distPlot <- renderPlot({
  x <- faithful[, 2]  # Old Faithful Geyser data
  bins <- seq(min(x), max(x), length.out = input$bins_a + 1)
  hist(x, breaks = bins, col = 'darkgray', border = 'white')
})
```

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}
2+2
```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
           answer("base"),
           answer("tools"),
           answer("utils", correct = TRUE),
           answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
           answer("lattice", correct = TRUE),
           answer("tools"),
           answer("stats"),
           answer("grid", correct = TRUE)
  )
)
```

