---
title: "Por que vemos pessoas vacinadas com covid-19?"
output: learnr::tutorial
runtime: shiny_prerendered
---

<!-- A fazer: marcados com TO-DO -->

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)
```
```{r general_parameters}
population_size = 1000
#TO-DO: percentual vacinado do Brasil
vacc_per_init = 30 #initial slider position for percentage of population vaccinated
#TO-DO: Percentual real para vacina selecionada
vacc_and_covid_prob = 0.35 #Only temporary number - Probability of being vaccinated and still get covid if exposed enough to get covid unvaccinated.
```

```{r data}
population = tibble(x = runif(population_size)*100, 
                    y = runif(population_size)*100,
                    covid_if_vacc = sample(x = c(TRUE,FALSE),
                                           replace = TRUE,
                                           size = population_size,
                                           prob = c(vacc_and_covid_prob,1-vacc_and_covid_prob)
                    )
)
```



## Com vacina, sem vacina e covid-19

Cada elemento no gráfico abaixo representa uma pessoa. Todas elas foram expostas ao vírus tempo suficiente para se infectar caso não tenham tomado a vacina.

Usando o controle, você pode determinar quantas delas estão vacinadas.

```{r vacc_per_control, echo=FALSE}
plotOutput("plot_vacc_non_vacc")
sliderInput("vacc_per", "Percentual vacinado da população:", min = 0, max = 100, value = vacc_per_init)
```

```{r plot_vacc_non_vacc, context="server"}
output$plot_vacc_non_vacc <- renderPlot({
  #TO-DO:Gráfico WAFFLE
  population %>%
    ggplot(aes(x=x, y=y, color = x > input$vacc_per)) +
    geom_point() 
  
})
```

<!-- #TO-DO:Texto explicando que mesmo com vacina pode covid -->
Mesmo com vacina, pode ter covid..... 

```{r vacc_non_vacc_covid, echo=FALSE}
plotOutput("plot_vacc_non_vacc_covid")
```

```{r plot_vacc_non_vacc_covid, context="server"}
output$plot_vacc_non_vacc_covid <- renderPlot({
  #TO-DO:Gráfico WAFFLE Padronizado
  population %>%
    mutate( sick = (x > input$vacc_per | covid_if_vacc)) %>%  #sick, if not vacc or if vacc but still in prob.
    ggplot(aes(x=x, y=y, 
               color = x > input$vacc_per, #color indicates vaccinated or not - change
               shape = sick)) +
    geom_point(size = 5) 
})
```

<!-- #TO-DO:Texto Introdução gráfico só com os doentes -->
Só os doentes

```{r covid_only, echo=FALSE}
plotOutput("plot_covid_only")
```

```{r plot_covid_only, context="server"}
output$plot_covid_only <- renderPlot({
  #TO-DO:Gráfico WAFFLE Padronizado
  population %>%
    mutate( sick = (x > input$vacc_per | covid_if_vacc)) %>% #sick, if not vacc or if vacc but still in prob.
    filter(sick) %>%
    ggplot(aes(x=x, y=y, 
               color = x > input$vacc_per, #color indicates vaccinated or not - change
               shape =  sick 
    )) +
    geom_point(size = 5) #TO-DO: adjust size? 
  
})
```


# Código exemplo a partir daqui - apagar ao final

```{r, echo=FALSE}
sliderInput("bins", "Number of bins:", min = 1, max = 50, value = 30)
plotOutput("distPlot")
```

```{r, context="server"}
output$distPlot <- renderPlot({
  x <- faithful[, 2]  # Old Faithful Geyser data
  bins <- seq(min(x), max(x), length.out = input$bins + 1)
  hist(x, breaks = bins, col = 'darkgray', border = 'white')
})
```

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}
2+2
```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
           answer("base"),
           answer("tools"),
           answer("utils", correct = TRUE),
           answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
           answer("lattice", correct = TRUE),
           answer("tools"),
           answer("stats"),
           answer("grid", correct = TRUE)
  )
)
```

